---
title: "UvA-BiTS Warehouse"
author: "Bart Aelterman <bart.aelterman@inbo.be>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=6, fig.path='Figs/',
                      warning=FALSE, message=FALSE, cache=TRUE)
library(UvaBitsWarehouse)
library(data.table)
library(ggplot2)
library(lubridate)
```

# Performance optimisation

This vignette examines the performance of different computations implemented in the UvaBitsWarehouse package.

## Date time parsing

During first profiling rounds, the slowest step turned out to be the date time parsing that happens during tracking data validation. Initially, lubridate's `ymd_hms` function was used but this turned out to be slow:

```{r date_time_parsing}
times <- c("2015-04-20 12:32:44", "2015-04-21 12:32:44", "2015-04-22 15:32:44",
					 "2015-04-22 12:32:44", "2015-04-22 12:35:44", "2015-04-23 16:32:44",
					 "2015-04-23 12:32:44", "2015-04-20 12:32:44", "2015-04-25 18:32:44"
					 )

ymd_hms_time <- as.numeric(system.time(ymd_hms(times))[3])
fast_strptime_time <- as.numeric(system.time(fast_strptime(times, "%Y-%m-%d %H:%M:%OS"))[3])
q <- qplot(x=c("ymd_hms", "fast_strptime"), y=c(ymd_hms_time, fast_strptime_time))
q + geom_point()
```

(See figure [here](Figs/date_time_parsing-1.png))

So, `ymd_hms` was replaced by `fast_strptime`. This cut off 73% of the `track_validation` step processing time.

## Profiling the different UvABiTSWarehouse steps


```{r profile}
d <- profiling_L1("../data/bird_track_logs_2000L.csv", "../data/two_birds.csv")
q <- qplot(x=d$step, y=d$timing)
q + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

(if the image isn't shown, view it [here](./Figs/profile-1.png))

After further investigation of the `validate_tracks_data` function, this turns out to be due to the fact that parsing date_times is slow.